---
title: "Biocrust Microbial Taxa"
author: "Brianne"
date: "2/25/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load libraries}
library(tidyverse)
library(MASS)
library(lme4)
library(car)
library(emmeans)
library(multcomp)
library(ggpubr)
library(rcompanion)
library(calecopal)
library(MuMIn)
library(vegan)
library(pairwiseAdonis)
```

```{r microbial community}

all.taxa <- read.csv("C:/Users/Brianne/Documents/San-Clemente-Biocrust-/data/taxon_rel_abund_edited_Feb2021.csv")

genus <- all.taxa %>%  dplyr::select(genus, X1:X24)
head(genus)

genus <- aggregate(. ~ genus, transform(genus, genus = genus), sum)

# The first column is actually the row names
rownames(genus) <- genus$genus
genus$genus <- NULL
head(genus)
genus.transposed <- as.data.frame(t(as.matrix(genus)))
rownames(genus.transposed) <- colnames(genus)
colnames(genus.transposed) <- rownames(genus)

metadata <- read.csv("C:/Users/Brianne/Documents/San-Clemente-Biocrust-/data/metadata.csv")
metadata <- metadata[c(1:24),]
genus.all <- as.data.frame(c(metadata, genus.transposed))
genus.all <- genus.all %>% rename(Sample = ï..Sample)
bsc <- genus.all

```

```{r all genera}
genus.only <- genus.all[,-c(1:90)]
genus.sums.long <- gather(genus.only, genus, n, 1:940)
sum_genus <- aggregate(n ~ genus, data=genus.sums.long, sum)

genera  <- sum_genus$genus [order (sum_genus$n, decreasing = TRUE)]

genera.order <- subset(sum_genus, genus %in% genera[1:200])

ggplot(data = genera.order, aes(x = reorder(genus,-n), y = n)) + geom_bar(stat = "identity", fill = "darkorchid4") + theme_bw() + coord_flip() + theme(legend.position = "none", axis.text.x = element_text(hjust = .9), text = element_text(size= 10)) + labs(x = "Abundance", y = "genus", title = "Top 200 genus")

```

This code will run a for loop to determine which genera varied with treatment. I haven't figure out how to do this in R yet but to figure out if there were any genera that differed, I called the list of genera with rownames(genera) then copired and pasted that and the p values from this fore loop into an excel sheet. Not very graceful, but it works..
```{r}

genus <- genus.all[c(91:1030)]
genus[is.na(genus)] <- 0
metadata <- genus.all[c(1:90)]

for(genus in genus){
  eq <- lm(genus ~ metadata$treatment)
  aov.p.value <- summary(aov(eq))[[1]]$'Pr(>F)'
  print(aov.p.value)
} 


```


```{r cyano}

cyano <- all.taxa %>% filter(phylum == "Cyanobacteria") %>%  dplyr::select(genus, bsc1:bsc24)

cyano <- aggregate(. ~ genus, transform(cyano, genus = genus), sum)

# The first column is actually the row names
rownames(cyano) <- cyano$genus
cyano$genus <- NULL
cyano.transposed <- as.data.frame(t(as.matrix(cyano)))
rownames(cyano.transposed) <- colnames(cyano)
colnames(cyano.transposed) <- rownames(cyano)

metadata <- metadata[c(1:24),]
cyano.all <- as.data.frame(c(metadata, cyano.transposed))
cyano.all <- genus.all %>% rename(Sample = ï..Sample)

genus <- cyano.all[c(91:113)]
genus[is.na(genus)] <- 0
metadata <- cyano.all[c(1:90)]

for(genus in genus){
  eq <- lm(genus ~ metadata$treatment)
  aov.p.value <- summary(aov(eq))[[1]]$'Pr(>F)'
  print(aov.p.value)
} 

cyano.pge <- cyano.all %>% filter(site == "pge")
genus <- cyano.pge[c(91:113)]
genus[is.na(genus)] <- 0
metadata <- cyano.pge[c(1:90)]
                      
for(genus in genus){
  eq <- lm(genus ~ metadata$treatment)
  aov.p.value <- summary(aov(eq))[[1]]$'Pr(>F)'
  print(aov.p.value)
} 

cyano.pgw <- cyano.all %>% filter(site == "pgw")
genus <- cyano.pgw[c(91:113)]
genus[is.na(genus)] <- 0
metadata <- cyano.pgw[c(1:90)]
                      
for(genus in genus){
  eq <- lm(genus ~ metadata$treatment)
  aov.p.value <- summary(aov(eq))[[1]]$'Pr(>F)'
  print(aov.p.value)
} 

cyano.rc <- cyano.all %>% filter(site == "rc")
genus <- cyano.rc[c(91:113)]
genus[is.na(genus)] <- 0
metadata <- cyano.rc[c(1:90)]
                      
for(genus in genus){
  eq <- lm(genus ~ metadata$treatment)
  aov.p.value <- summary(aov(eq))[[1]]$'Pr(>F)'
  print(aov.p.value)
} 

genus <- cyano.all[c(91:113)]
genus[is.na(genus)] <- 0
metadata <- cyano.all[c(1:90)]

for(genus in genus){
  eq <- lm(genus ~ metadata$site)
  aov.p.value <- summary(aov(eq))[[1]]$'Pr(>F)'
  print(aov.p.value)
} 


```


```{r microbial commmunity nmds}

genus.only <- genus.all[-c(1:90)]

genus.nmds <- metaMDS(genus.only, trace = FALSE, trymax=100, "bray")
genus.nmds$stress 

# make the NMDS plot and analyze dissimilarities 

#build a data frame with NMDS coordinates and metadata 
MDS1 = genus.nmds$points[,1] # adds the points of the NMDS 1 dimmension
MDS2 = genus.nmds$points[,2] # adds the points of the NMDS 2 dimmension

metadata$FireType <- c("prescribed","prescribed","prescribed","prescribed","control", "control", "control", "control","prescribed","prescribed","prescribed","prescribed","control", "control", "control", "control", "wildfire", "wildfire", "wildfire", "wildfire", "control", "control", "control", "control")

NMDS = data.frame(MDS1 = MDS1, MDS2 = MDS2, treatment = metadata$treatment, site = metadata$site, FireType = metadata$FireType) # this builds a dataframe with the NMDS dimmensions, treatment, site, and burn year 

# make the NMDS plot
ggplot(NMDS, aes(x = MDS1, y = MDS2, col = site)) + geom_point() + 
  stat_ellipse() + theme_bw()

# determine if the differene is significant by doing a PERMANOVA
adonis(genus.only ~ FireType, metadata) 

pairwise.adonis(genus.only,factors=metadata$FireType)
pairwise.adonis(genus.only,factors=metadata$treatment)
pairwise.adonis(genus.only,factors=metadata$site)

env <- metadata[c(7:90)]

env.fit <- envfit(genus.nmds,env , permutations = 999, na.rm = TRUE)

env.fit$vectors

```

Make stacked bar plots and heat maps 

```{r}

all.taxa[c(7:30)] <- sapply(all.taxa[c(7:30)],as.numeric)
all.taxa$Sum <-rowSums(all.taxa[c(7:30)]) 
one_percent <- all.taxa %>% filter(Sum < 0.01)
one_percent_summed <- colSums(one_percent[c(7:30)])
one_percent <- one_percent %>%  dplyr::select(genus, bsc1:bsc24)
head(one_percent)
one_percent <- aggregate(. ~ genus, transform(one_percent, genus = genus), sum)
rownames(one_percent) <- one_percent$genus
one_percent$genus <- NULL
head(one_percent)
one_percent.transposed <- as.data.frame(t(as.matrix(one_percent)))
rownames(one_percent.transposed) <- colnames(one_percent)
colnames(one_percent.transposed) <- rownames(one_percent)
remove <- colnames(one_percent.transposed)
genus.df <- genus.all[-which(names(genus.all) %in% remove)]
less_1_percent <- rowSums(one_percent.transposed)
genus.df$less_1_percent <- less_1_percent

remove.2 <- one_percent$genus
all.taxa.df <- all.taxa %>% filter(!genus %in% remove)

one_percent_vector <- c("One Percent", "One Percent", "One Percent", "One Percent", "One Percent", "One Percent", rowSums(one_percent[1:24]))

all.taxa.df <- rbind(all.taxa.df, one_percent_vector)

phylum <- all.taxa.df %>%  dplyr::select(phylum, bsc1:bsc24)
head(phylum)
phylum[c(2:25)] <- sapply(phylum[c(2:25)],as.numeric)
phylum <- aggregate(. ~ phylum, transform(phylum, phylum = phylum), sum)
rownames(phylum) <- phylum$phylum
phylum$phylum <- NULL
head(phylum)
phylum.transposed <- as.data.frame(t(as.matrix(phylum)))
rownames(phylum.transposed) <- colnames(phylum)
colnames(phylum.transposed) <- rownames(phylum)

metadata <- read.csv("C:/Users/Brianne/OneDrive - San Diego State University (SDSU.EDU)/R WorkBooks/metagenomics/data/metadata.csv")
metadata <- metadata[c(1:24),]
phylum.all <- as.data.frame(c(metadata, phylum.transposed))
phylum.all[c(91:112)] <- sapply(phylum.all[c(91:112)],as.numeric)
phylum.ggplot <- pivot_longer(phylum.all, cols = Acidobacteria:Verrucomicrobia, names_to = "phylum", values_to = "count")
phylum.ggplot$Sample <- phylum.ggplot$ï..Sample

phylum_pal <- cal_palette(name = "dudleya", n = 22, type = "continuous")


ggplot(phylum.ggplot, aes(fill = phylum, y = count, x = treatment)) + geom_bar(position = "fill", stat = "identity") + facet_wrap(.~ site) + theme_bw() + scale_fill_manual(values = phylum_pal)

```

```{r}

cyanobacteria <- all.taxa.df %>%  filter(phylum == "Cyanobacteria") %>% dplyr::select(genus, bsc1:bsc24)
cyanobacteria[c(2:25)] <- sapply(cyanobacteria[c(2:25)],as.numeric)
cyanobacteria <- aggregate(. ~ genus, transform(cyanobacteria, genus = genus), sum)
rownames(cyanobacteria) <- cyanobacteria$genus
cyanobacteria$genus <- NULL
cyanobacteria.transposed <- as.data.frame(t(as.matrix(cyanobacteria)))
rownames(cyanobacteria.transposed) <- colnames(cyanobacteria)
colnames(cyanobacteria.transposed) <- rownames(cyanobacteria)

cyanobacteria.all <- as.data.frame(c(metadata, cyanobacteria.transposed))
cyanobacteria.all[c(91:106)] <- sapply(cyanobacteria.all[c(91:106)],as.numeric)
cyanobacteria.ggplot <- pivot_longer(cyanobacteria.all, cols = Acaryochloris:Trichodesmium, names_to = "genus", values_to = "count")
cyanobacteria.ggplot$Sample <- cyanobacteria.ggplot$ï..Sample


ggplot(cyanobacteria.ggplot, aes(fill = genus, y = count, x = treatment)) + geom_bar(position = "fill", stat = "identity") + facet_wrap(.~ site) + theme_bw()

```

```{r}

ascomycota <- all.taxa.df %>%  filter(phylum == "Ascomycota") %>% dplyr::select(genus, bsc1:bsc24)
ascomycota[c(2:25)] <- sapply(ascomycota[c(2:25)],as.numeric)
ascomycota <- aggregate(. ~ genus, transform(ascomycota, genus = genus), sum)
rownames(ascomycota) <- ascomycota$genus
ascomycota$genus <- NULL
ascomycota.transposed <- as.data.frame(t(as.matrix(ascomycota)))
rownames(ascomycota.transposed) <- colnames(ascomycota)
colnames(ascomycota.transposed) <- rownames(ascomycota)

ascomycota.all <- as.data.frame(c(metadata, ascomycota.transposed))
ascomycota.all[c(91:111)] <- sapply(ascomycota.all[c(91:111)],as.numeric)
ascomycota.ggplot <- pivot_longer(ascomycota.all, cols = Ajellomyces:Uncinocarpus, names_to = "genus", values_to = "count")
ascomycota.ggplot$Sample <- ascomycota.ggplot$ï..Sample




ggplot(ascomycota.ggplot, aes(fill = genus, y = count, x = treatment)) + geom_bar(position = "fill", stat = "identity") + facet_wrap(.~ site) + theme_bw()


```

```{r}
phylum <- all.taxa.df %>% dplyr::select(phylum, bsc1:bsc24)
phylum[c(2:25)] <- sapply(phylum[c(2:25)],as.numeric)
phylum <- aggregate(. ~ phylum, transform(phylum, phylum = phylum), sum)
rownames(phylum) <- phylum$phylum
phylum$phylum <- NULL
phylum.transposed <- as.data.frame(t(as.matrix(phylum)))
rownames(phylum.transposed) <- colnames(phylum)
colnames(phylum.transposed) <- rownames(phylum)

phylum.all <- as.data.frame(c(metadata, phylum.transposed))
phylum.all[c(91:111)] <- sapply(phylum.all[c(91:111)],as.numeric)
phylum.ggplot <- pivot_longer(phylum.all, cols = Acidobacteria:Verrucomicrobia, names_to = "phylum", values_to = "count")
phylum.ggplot$Sample <- phylum.ggplot$ï..Sample

numcols <- 22
phylum_cols <- colorRampPalette(brewer.pal(8, "Set1"))(numcols)


ggplot(phylum.ggplot, aes(fill = phylum, y = count, x = treatment)) + geom_bar(position = "fill", stat = "identity") + facet_wrap(.~ site) + theme_bw() + scale_fill_manual(values = phylum_cols)

Anova(lm(One.Percent ~ treatment* site, data = phylum.all)) # differs by site 
Anova(lm(Planctomycetes ~ treatment* site, data = phylum.all)) # differs by site, almost by treatment

```

```{r heat map}

phylum.all$sample <- phylum.all$ï..Sample
heatmap <- phylum.all %>% dplyr::select(site, treatment,sample,Acidobacteria:Verrucomicrobia)
row.names(heatmap) <- heatmap$sample
rowsidecolors <- c("red","red", "red", "red", "blue", "blue", "blue", "blue","red","red", "red", "red", "blue", "blue", "blue", "blue","red","red", "red", "red", "blue", "blue", "blue", "blue")
heatmap <- heatmap[-c(1:3)]
heatmap <- as.matrix(heatmap)
heatmap(heatmap, na.rm = FALSE, scale = "column", Colv = NA, Rowv = NA, RowSideColors = rowsidecolors)

# burn only 
heatmap <- phylum.all %>% filter(treatment == "burn") %>%  dplyr::select(site, treatment,sample,Acidobacteria:Verrucomicrobia)
row.names(heatmap) <- heatmap$sample
heatmap <- heatmap[-c(1:3)]
heatmap <- as.matrix(heatmap)
heatmap(heatmap, na.rm = FALSE, scale = "column", Colv = NA, Rowv = NA)


```


```{r combine cover and cyanobacteria}

cyanocover <- data %>% filter(Sample.Year =="2018", Treatment != "rx/wild")
cyanocover <- cyanocover[-c(253:280),]
cyanocover.short <- cyanocover %>% group_by(Site, Treatment) %>% summarize_at(vars(cyano:Total),list(mean = mean))

cyanobacteria.short <- cyanobacteria.all %>% group_by(treatment, site) %>% summarize_at(vars(Acaryochloris:Trichodesmium), list(mean=mean))

cyanocover.short$treatment <- cyanocover.short$Treatment
cyanocover.short$site <- cyanocover.short$Site
cyanobacteria.short$treatment <- c("rx", "rx", "wild", "none", "none", "none")

hist(log(cyano.cover.micro$Total_mean))

cyano.cover.micro <- merge(cyanocover.short, cyanobacteria.short, by = c("treatment", "site"))
cyano.cover.micro$cyanoTotal <- sum(cyano.cover.micro$Acaryochloris_mean:cyano.cover.micro$Trichodesmium_mean)
total_cyano_mod <- lm(cyano_mean ~ Microcoleus_mean, data = cyano.cover.micro)
Anova(total_cyano_mod) 

# [1] "treatment"                "site"                     "Acaryochloris_mean"      
# [4] "Anabaena_mean"            "Arthrospira_mean"         "Crocosphaera_mean"       
# [7] "Cyanothece_mean"          "Gloeobacter_mean"         "Lyngbya_mean"            
# [10] "Microcoleus_mean"         "Microcystis_mean"         "Nodularia_mean"          
# [13] "Nostoc_mean"              "Oscillatoria_mean"        "Synechococcus_mean"      
# [16] "Synechocystis_mean"       "Thermosynechococcus_mean" "Trichodesmium_mean" 


ggplot(data = cyano.cover.micro, aes(x = cyano_mean, y = Microcoleus_mean)) + geom_point() + theme_bw()


```

```{r }

ascomycota.short <- ascomycota.all %>% group_by(treatment, site) %>% summarize_at(vars(Ajellomyces:Uncinocarpus), list(mean=mean))
ascomycota.short$treatment <- c("rx", "rx", "wild", "none", "none", "none")

lichen.cover.micro <- merge(cyanocover.short, ascomycota.short, by = c("treatment", "site"))
lichen.cover.micro$lichenTotal <- sum(lichen.cover.micro$Ajellomyces_mean:lichen.cover.micro$Uncinocarpus_mean)

total_lichen_mod <- lm(Lichen_mean ~ Penicillium_mean^2, data = lichen.cover.micro)
Anova(total_lichen_mod) 

#  [1] "treatment"             "site"                  "Ajellomyces_mean"     
# [4] "Arthroderma_mean"      "Aspergillus_mean"      "Botryotinia_mean"     
 #[7] "Chaetomium_mean"       "Coccidioides_mean"     "Emericella_mean"      
#[10] "Gibberella_mean"       "Magnaporthe_mean"      "Nectria_mean"         
#[13] "Neosartorya_mean"      "Neurospora_mean"       "Paracoccidioides_mean"
#[16] "Penicillium_mean"      "Phaeosphaeria_mean"    "Podospora_mean"       
#[19] "Pyrenophora_mean"      "Sclerotinia_mean"      "Talaromyces_mean"     
#[22] "Tuber_mean"            "Uncinocarpus_mean" 
formula <- lichen.cover.micro$Lichen_mean ~ lichen.cover.micro$Penicillium_mean^2
ggplot(data = lichen.cover.micro, aes(x = Lichen_mean, y = Penicillium_mean)) + geom_point() + theme_bw() + geom_smooth()

```

```{r}
# find the percentage of each group 

View(all.taxa)
all.taxa$domain <- all.taxa$ï..domain
archaea <- all.taxa %>% filter(domain == "Archaea")
bacteria <- all.taxa %>% filter(domain == "Bacteria")
eukaryota <- all.taxa %>% filter(domain =="Eukaryota")
viruses <- all.taxa %>% filter(domain == "Viruses")

per.archaea = (sum(archaea[7:30])/sum(all.taxa[7:30]))*100 # 0.5 % Archaea
per.bacteria = (sum(bacteria[7:30])/sum(all.taxa[7:30]))*100 # 91.14 % Bacteria
per.eukaryota = (sum(eukaryota[7:30])/sum(all.taxa[7:30]))*100 # 6.26% Eukaryote
per.viruses = (sum(viruses[7:30])/sum(all.taxa[7:30]))*100 # 2.10% viruses 

actino <- all.taxa %>% filter(phylum == "Actinobacteria")
sum(actino[7:30])/sum(all.taxa[7:30])

proteo <- all.taxa %>% filter(phylum == "Proteobacteria")
sum(proteo[7:30])/sum(all.taxa[7:30])

cyano <- all.taxa %>% filter(phylum == "Cyanobacteria")
sum(cyano[7:30])/sum(all.taxa[7:30])



```
