---
title: "Random Forest"
author: "Brianne"
date: "2/26/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load libraries}
library(tidyverse)
library(randomForest)
library(dismo)
library(gbm)
```

The next step is to load the data for bulk (Ben's SCI), biocrust, and plants. Since there are different number of rows for each dataset, when I upload them, I also adjust the row numbers to match. For bulk and bsc, I am only using the top 200 most abundant genera 

```{r bulk data}
bulk <- read.csv("C:/Users/Brianne/OneDrive - San Diego State University (SDSU.EDU)/R WorkBooks/metagenomics/data/Ben_sci_taxon_rel_abund.csv")
bulk.metadata <- read.csv("C:/Users/Brianne/OneDrive - San Diego State University (SDSU.EDU)/R WorkBooks/metagenomics/data/metadata_bulk.csv")

bulk.genus <- bulk %>%  dplyr::select(genus, bulk1:bulk40)

bulk.genus <- aggregate(. ~ genus, transform(bulk.genus, genus = genus), sum)

# The first column is actually the row names
rownames(bulk.genus) <- bulk.genus$genus
bulk.genus$genus <- NULL
head(bulk.genus)
bulk.genus.transposed <- data.frame(t((bulk.genus)))
rownames(bulk.genus.transposed) <- colnames(bulk.genus)
colnames(bulk.genus.transposed) <- rownames(bulk.genus)

bulk.all <- as.data.frame(c(bulk.metadata, bulk.genus.transposed))
bulk.all <- bulk.all %>% rename(Sample = 誰..Sample)
bulk.all <- bulk.all[-c(1,23,34,40,45, 17, 30,9),]


bulk.genus.only <- bulk.all[-c(1:90)]
bulk.genus.sums.long <- gather(bulk.genus.only, genus, n, 1:1117)
bulk.genus.sums.long$n <- as.numeric(bulk.genus.sums.long$n)
bulk.sum_genus <- aggregate(n ~ genus, data=bulk.genus.sums.long, sum)

bulk.genera  <- bulk.sum_genus$genus [order (bulk.sum_genus$n, decreasing = TRUE)]
bulk.genera.order <- subset(bulk.sum_genus, genus %in% bulk.genera[1:200])

bulk.names <- bulk.genera.order$genus
bulk.name.use <- bulk.genus.only[names(bulk.genus.only) %in% bulk.names]
bulk <- data.frame(bulk.all[-c(91:1207)], bulk.name.use)
```


```{r bsc data}

all.taxa <- read.csv("C:/Users/Brianne/Documents/San-Clemente-Biocrust-/data/taxon_rel_abund_edited_Feb2021.csv")
metadata <- read.csv("C:/Users/Brianne/Documents/San-Clemente-Biocrust-/data/metadata.csv")
metadata <- metadata[c(1:24),]

bsc.genus <- all.taxa %>%  dplyr::select(genus, X1:X24)

# The first column is actually the row names
rownames(bsc.genus) <- bsc.genus$genus
bsc.genus$genus <- NULL
bsc.genus.transposed <- data.frame(t((bsc.genus)))
rownames(bsc.genus.transposed) <- colnames(bsc.genus)
colnames(bsc.genus.transposed) <- rownames(bsc.genus)

bsc.all <- as.data.frame(c(metadata, bsc.genus.transposed))
bsc.all <- bsc.all %>% rename(Sample = 誰..Sample)

bsc.genus.only <- bsc.all[-c(1:90)]
bsc.genus.sums.long <- gather(bsc.genus.only, genus, n, 1:940)
bsc.genus.sums.long$n <- as.numeric(bsc.genus.sums.long$n)
bsc.sum_genus <- aggregate(n ~ genus, data=bsc.genus.sums.long, sum)

bsc.genera  <- bsc.sum_genus$genus [order (bsc.sum_genus$n, decreasing = TRUE)]
bsc.genera.order <- subset(bsc.sum_genus, genus %in% bsc.genera[1:200])

bsc.names <- bsc.genera.order$genus
bsc.name.use <- bsc.genus.only[names(bsc.genus.only) %in% bsc.names]
bsc <- data.frame(metadata,bsc.name.use)

```

```{r macro and plants}
macro <- read.csv("C:/Users/Brianne/OneDrive - San Diego State University (SDSU.EDU)/R WorkBooks/BSC_SCI/biocrust/data/sci_bsc_2018_2019.csv")

macro <- macro %>% filter(Sample.Year == "2018", Site != "rc")

plants <- read.csv("C:/Users/Brianne/OneDrive - San Diego State University (SDSU.EDU)/R WorkBooks/SCI Plants/data/all_plants.csv")
plants <- plants %>% filter(Year == 2018, Site != "RC") 
plants$Cover <- as.numeric(plants$Cover)
ng.cov <- plants %>% filter(Funct.Gp == "ng") %>% mutate(ng.cov = mean(Cover))
plants <- merge(plants, ng.cov, all = TRUE)
nng.cov <- plants %>% filter(Funct.Gp == "nng") %>% mutate(nng.cov = mean(Cover))
plants <- merge(plants, nng.cov, all = TRUE)
nnf.cov <- plants %>% filter(Funct.Gp == "nnf") %>% mutate(nnf.cov = mean(Cover))
plants <- merge(plants, nnf.cov, all = TRUE)
nf.cov <- plants %>% filter(Funct.Gp == "nf") %>% mutate(nf.cov = mean(Cover))
plants <- merge(plants, nf.cov, all = TRUE)
plants[is.na(plants)] <- 0
plants$ID <- plants$誰..Ref

plants$Cover <- as.numeric(plants$Cover)
plants <- plants %>% group_by(Site, Treatment, Quad, Year, Code, ID)
plants <- plants %>% pivot_wider(names_from = Code, values_from = Cover, values_fn = list(Cover = mean))

plants[is.na(plants)] <- 0
 #this is goving me a weird number of rows, need to redo , see the Random Forest r workbook

plants <- plants %>% group_by(Site, Treatment, Year, ID, Quad) %>% summarize_at(vars(ng.cov:VIOPED),list(mean = mean))
```

Combine the datasets together in pairs 

Make Macro-Plant
```{r}

#plants is missing PGE burn 1 B, PGEB2C
macro_rm <- macro[-c(2,7),]
macro_plant <- data.frame(macro_rm, plants)


macro_plant$Treatment <- as.factor(macro_plant$Treatment)
macro_plant$Site <- as.factor(macro_plant$Site)

```

Make Macro-BSC
```{r}
macro_short <- macro %>% dplyr::select(Site, Treatment, Per.Cyano, Per.Lichen, Per.Moss, Per.Total) %>% 
    group_by(Site, Treatment) %>% summarize(Per.Cyano = mean(Per.Cyano), Per.Lichen = mean(Per.Lichen), Per.Moss = mean(Per.Moss), Per.Total = mean(Per.Total))

pgwburn <- data.frame(rbind(macro_short[3,],macro_short[3,],macro_short[3,],macro_short[3,]))
pgwcont <- data.frame(rbind(macro_short[4,],macro_short[4,],macro_short[4,],macro_short[4,]))
pgeburn <- data.frame(rbind(macro_short[1,],macro_short[1,],macro_short[1,],macro_short[3,]))
pgecont <- data.frame(rbind(macro_short[2,],macro_short[2,],macro_short[2,],macro_short[4,]))
rcburn <- data.frame(rbind(macro_short[5,],macro_short[5,],macro_short[5,],macro_short[5,]))
rccont <- data.frame(rbind(macro_short[6,],macro_short[6,],macro_short[6,],macro_short[6,]))

macro_short <-data.frame(rbind(pgwburn, pgwcont, pgeburn, pgecont, rcburn, rccont))

macro_bsc <- data.frame(macro_short, bsc)
```

```{r make bsc macro }
bsc_macro <- bsc %>% 
    group_by(site, treatment) %>% summarize_at(vars(Methanosarcina:Microvirus),list(mean = mean))

n <- 40

pgwburn <- do.call("rbind", replicate(n, bsc_macro[3,], simplify = FALSE))
pgwcont <- do.call("rbind", replicate(n, bsc_macro[4,], simplify = FALSE))
pgeburn <- do.call("rbind", replicate(n, bsc_macro[1,], simplify = FALSE))
pgecont <-do.call("rbind", replicate(n, bsc_macro[2,], simplify = FALSE))

n <- 80
rcburn <- do.call("rbind", replicate(n, bsc_macro[5,], simplify = FALSE))
rccont <- do.call("rbind", replicate(n, bsc_macro[6,], simplify = FALSE))
bsc_macro <- data.frame(rbind(pgeburn, pgecont, pgwburn, pgwcont,rcburn, rccont))
bsc_macro <- data.frame(bsc_macro, macro)

```

Make Macro-Bulk
```{r}
# remove RC because Ben did not sample RC 

macro <- macro %>% filter(Sample.Year == "2018", Site != "rc")

bulk_long <- bulk %>% 
    group_by(site, treatment) %>% summarize_at(vars(Achromobacter:Zymomonas),list(mean = mean))


n <- 40

pgwburn <- do.call("rbind", replicate(n, bulk_long[3,], simplify = FALSE))
pgwcont <- do.call("rbind", replicate(n, bulk_long[4,], simplify = FALSE))
pgeburn <- do.call("rbind", replicate(n, bulk_long[1,], simplify = FALSE))
pgecont <-do.call("rbind", replicate(n, bulk_long[2,], simplify = FALSE))

bulk_long <- data.frame(rbind(pgeburn, pgecont, pgwburn, pgwcont))


macro_bulk <- data.frame(macro, bulk_long)

```

Make Plant- BSC
```{r}

bsc.pg <- bsc %>% filter(site != "rc")
plants <- read.csv("C:/Users/Brianne/OneDrive - San Diego State University (SDSU.EDU)/R WorkBooks/SCI Plants/data/all_plants.csv")
plants <- plants %>% filter(Year == 2018, Site != "RC") 
plants$Cover <- as.numeric(plants$Cover)
ng.cov <- plants %>% filter(Funct.Gp == "ng") %>% mutate(ng.cov = mean(Cover))
plants <- merge(plants, ng.cov, all = TRUE)
nng.cov <- plants %>% filter(Funct.Gp == "nng") %>% mutate(nng.cov = mean(Cover))
plants <- merge(plants, nng.cov, all = TRUE)
nnf.cov <- plants %>% filter(Funct.Gp == "nnf") %>% mutate(nnf.cov = mean(Cover))
plants <- merge(plants, nnf.cov, all = TRUE)
nf.cov <- plants %>% filter(Funct.Gp == "nf") %>% mutate(nf.cov = mean(Cover))
plants <- merge(plants, nf.cov, all = TRUE)
plants <- plants %>% pivot_wider(names_from = Code, values_from = Cover, values_fn = list(Cover = mean)) 
plants[is.na(plants)] <- 0
plants_short <- plants %>% group_by(Site, Treatment, Year) %>% summarize_at(vars(ng.cov:VIOPED),list(mean = mean))

pgwburn <- data.frame(rbind(plants_short[3,],plants_short[3,],plants_short[3,],plants_short[3,]))
pgwcont <- data.frame(rbind(plants_short[4,],plants_short[4,],plants_short[4,],plants_short[4,]))
pgeburn <- data.frame(rbind(plants_short[1,],plants_short[1,],plants_short[1,],plants_short[1,]))
pgecont <- data.frame(rbind(plants_short[2,],plants_short[2,],plants_short[2,],plants_short[2,]))

plants_short <- data.frame(rbind(pgwburn, pgwcont, pgeburn, pgecont))

bsc_plant <- data.frame(plants_short, bsc.pg)


bsc_short <- bsc.pg %>% group_by(site, treatment) %>% summarize_at(vars(Methanosarcina:Microvirus), list(mean = mean))

n <- 10

pgwburn <- do.call("rbind", replicate(n, bsc_short[3,], simplify = FALSE))
pgwcont <- do.call("rbind", replicate(n, bsc_short[4,], simplify = FALSE))
pgeburn <- do.call("rbind", replicate(n, bsc_short[1,], simplify = FALSE))
pgecont <-do.call("rbind", replicate(n, bsc_short[2,], simplify = FALSE))

bsc_short <- data.frame(rbind(pgeburn, pgecont, pgwburn, pgwcont))
plants <- read.csv("C:/Users/Brianne/OneDrive - San Diego State University (SDSU.EDU)/R WorkBooks/SCI Plants/data/all_plants.csv")
plants <- plants %>% filter(Year == 2018, Site != "RC") 
plants$Cover <- as.numeric(plants$Cover)
ng.cov <- plants %>% filter(Funct.Gp == "ng") %>% mutate(ng.cov = mean(Cover))
plants <- merge(plants, ng.cov, all = TRUE)
nng.cov <- plants %>% filter(Funct.Gp == "nng") %>% mutate(nng.cov = mean(Cover))
plants <- merge(plants, nng.cov, all = TRUE)
nnf.cov <- plants %>% filter(Funct.Gp == "nnf") %>% mutate(nnf.cov = mean(Cover))
plants <- merge(plants, nnf.cov, all = TRUE)
nf.cov <- plants %>% filter(Funct.Gp == "nf") %>% mutate(nf.cov = mean(Cover))
plants <- merge(plants, nf.cov, all = TRUE)
plants <- plants %>% pivot_wider(names_from = Code, values_from = Cover, values_fn = list(Cover = mean)) 
plants[is.na(plants)] <- 0
plants$ID <- plants$誰..Ref
plants <-  plants %>% group_by(Site, Treatment, Year, ID) %>% summarize_at(vars(ng.cov:VIOPED),list(mean = mean))

plant_bsc <- data.frame(bsc_short, plants)

```

Make Plant-Bulk
```{r}

plant_bulk <- data.frame(plants, bulk)

```

Make BSC - Bulk

```{r}


bulk <- bulk %>% mutate_at(c(91:290), as.numeric)

bulk_short <- bulk %>% 
    group_by(site, treatment) %>% summarize_at(vars(Achromobacter:Zymomonas),list(mean = mean))

pgwburn <- data.frame(rbind(bulk_short[3,],bulk_short[3,],bulk_short[3,],bulk_short[3,]))
pgwcont <- data.frame(rbind(bulk_short[4,],bulk_short[4,],bulk_short[4,],bulk_short[4,]))
pgeburn <- data.frame(rbind(bulk_short[1,],bulk_short[1,],bulk_short[1,],bulk_short[3,]))
pgecont <- data.frame(rbind(bulk_short[2,],bulk_short[2,],bulk_short[2,],bulk_short[4,]))

bulk_short <- data.frame(rbind(pgwburn, pgwcont, pgeburn, pgecont))

bsc_bulk <- data.frame(bulk_short, bsc)
bsc_bulk <- bsc_bulk[-c(1121:1209)]

```

## Begin Random Forest Analysis 

```{r Random Forest for macro_plant}
#relative influence of plants on the total macro bsc cover 

macro_plant <- macro_plant %>% mutate_at(c(23:66), as.numeric)

rf <- randomForest(Per.Total ~ ., ntree = 1000, importance = TRUE, data = macro_plant[c(3,6,10,23:66)])

print(rf) # 32.49,32.17
VI_F = importance(rf)
varImpPlot(rf,type=1)
importanceOrder=order(-rf$importance)
names=rownames(rf$importance)[importanceOrder]

rf_pred <- predict(rf, macro_plant[c(3,6,10,23:66)]) # predictions
caret::postResample(rf_pred, macro_plant$Per.Total)

```

```{r rf for plant functional groups}

rf <- randomForest(Per.Total ~ ., ntree = 1000, importance = TRUE, data = macro_plant[c(3,6,10,19:22)])

print(rf)   
VI_F = importance(rf)
varImpPlot(rf,type=1)

rf_pred <- predict(rf, macro_plant[c(3,6,10,19:22)]) # predictions
caret::postResample(rf_pred, macro_plant$Per.Total)


```

```{r rf for influence of BSC microbes on BSC cover }

#relative influence of bsc microbes on the total macro bsc cover 


rf <- randomForest(Per.Total ~ ., ntree = 1000, importance = TRUE, data = bsc_macro[c(1:202, 212)])

print(rf)
VI_F = importance(rf)
varImpPlot(rf,type=1)

rf_pred <- predict(rf,bsc_macro[c(1:202, 212)]) # predictions
caret::postResample(rf_pred, bsc_macro$Per.Total)



```


```{r rf for influence of bulk microbes on BSC cover }

#relative influence of bulk microbes on the total macro bsc cover 
macro_bulk$Site <- as.factor(macro_bulk$Site)
macro_bulk$Treatment <- as.factor(macro_bulk$Treatment)
macro_bulk <- macro_bulk %>% mutate_at(c(16:215), as.numeric)

rf <- randomForest(Per.Total ~ ., ntree = 1000, importance = TRUE, data = macro_bulk[c(3,6,16:215,10)])

print(rf)
VI_F = importance(rf)
varImpPlot(rf,type=1)

rf_pred <- predict(rf,macro_bulk[c(3,6,16:215,10)]) # predictions
caret::postResample(rf_pred, macro_bulk$Per.Total)

```


```{r plant cover + bsc cover }

plant_bsc <- plant_bsc %>% mutate(plantCover = rowSums(.[211:254]))

rf <- randomForest(plantCover ~ ., ntree = 1000, importance = TRUE, data = plant_bsc[c(1:202,255)])
#51.3, 51.47

print(rf)
VI_F = importance(rf)
varImpPlot(rf,type=1)

rf_pred <- predict(rf,plant_bsc[c(1:202,255)]) # predictions
caret::postResample(rf_pred, plant_bsc$plantCover)



native_bsc <- plant_bsc %>% mutate(nativeCover = rowSums(.[207:208]))

rf <- randomForest(nativeCover ~ ., ntree = 1000, importance = TRUE, data = native_bsc[c(1:202,256)])
#51.3, 51.47

print(rf)
VI_F = importance(rf)
varImpPlot(rf,type=1)

rf_pred <- predict(rf,native_bsc[c(1:202,255)]) # predictions
caret::postResample(rf_pred, native_bsc$nativeCover)

nonnative_bsc <- plant_bsc %>% mutate(nonnativeCover = rowSums(.[209:210]))

rf <- randomForest(nonnativeCover ~ ., ntree = 1000, importance = TRUE, data = nonnative_bsc[c(1:202,256)])
#51.3, 51.47

print(rf)
VI_F = importance(rf)
varImpPlot(rf,type=1)

rf_pred <- predict(rf,nonnative_bsc[c(1:202,255)]) # predictions
caret::postResample(rf_pred, nonnative_bsc$nonnativeCover)


```

```{r plant cover + bulk microbe }

plant_bulk <- plant_bulk %>% mutate(plantCover = rowSums(.[9:52]))

rf <- randomForest(plantCover ~ ., ntree = 1000, importance = TRUE, data = plant_bulk[c(1,2,143:343)])


print(rf)
VI_F = importance(rf)
varImpPlot(rf,type=1)

rf_pred <- predict(rf,plant_bulk[c(1,2,143:343)]) # predictions
caret::postResample(rf_pred, plant_bulk$plantCover)
```


```{r random forest to determine burned/control from datasets}
library(caTools)
library(pROC)

macro$Treatment <- as.factor(macro$Treatment)
macro[is.na(macro)] <- 0

smp_size <- floor(0.75 * nrow(macro))
set.seed(123)
train_ind <- sample(seq_len(nrow(macro)), size = smp_size)
train <- macro[train_ind,]
test <- macro[-train_ind,]

rf <- randomForest(Treatment ~ ., ntree = 1000, importance = TRUE, data = train[c(6:10)])
print(rf)
varImpPlot(rf)
predicion_for_table <- predict(rf, test[,-6])
table(observed = test[,6], predicted = predicion_for_table)
rf.roc <- roc(train$Treatment, rf$votes[,2])
plot(rf.roc)
auc(rf.roc)

```

```{r rf bsc microbes and treatment }

bsc$treatment <- as.factor(bsc$treatment)
bsc[is.na(bsc)] <- 0

smp_size <- floor(0.75 * nrow(bsc))
set.seed(123)
train_ind <- sample(seq_len(nrow(bsc)), size = smp_size)
train <- bsc[train_ind,]
test <- bsc[-train_ind,]

rf <- randomForest(treatment ~ ., ntree = 1000, importance = TRUE, data = train[c(3,91:290)])
print(rf)
varImpPlot(rf)
predicion_for_table <- predict(rf, test[,-3])
table(observed = test[,3], predicted = predicion_for_table)
rf.roc <- roc(train$treatment, rf$votes[,2])
plot(rf.roc)
auc(rf.roc)


```

```{r rf bulk microbes and treatment }

bulk$treatment <- as.factor(bulk$treatment)
bulk[is.na(bulk)] <- 0

smp_size <- floor(0.75 * nrow(bulk))
set.seed(123)
train_ind <- sample(seq_len(nrow(bulk)), size = smp_size)
train <- bulk[train_ind,]
test <- bulk[-train_ind,]

rf <- randomForest(treatment ~ ., ntree = 1000, importance = TRUE, data = train[c(4,91:290)])
print(rf)
varImpPlot(rf)
predicion_for_table <- predict(rf, test[,-4])
table(observed = test[,4], predicted = predicion_for_table)
rf.roc <- roc(train$treatment, rf$votes[,2])
plot(rf.roc)
auc(rf.roc)


```

```{r rf plant and treatment }

plants$Treatment <- as.factor(plants$Treatment)
plants[is.na(plants)] <- 0

smp_size <- floor(0.75 * nrow(plants))
set.seed(123)
train_ind <- sample(seq_len(nrow(plants)), size = smp_size)
train <- plants[train_ind,]
test <- plants[-train_ind,]

rf <- randomForest(Treatment ~ ., ntree = 1000, importance = TRUE, data = train[c(2,9:52)])
print(rf)
varImpPlot(rf)
test$Treatment <- as.factor(test$Treatment)
predicion_for_table <- predict(rf, test[,-2])
table(observed = test[,2], predicted = predicion_for_table)
rf.roc <- roc(train$Treatment, rf$votes[,2])
plot(rf.roc)
auc(rf.roc)


```
```{r plot most important vaiables from rf and biocrust cover}

#PTEDRY

ggplot(data = macro_plant, aes(x = Per.Total, y = PTEDRY_mean)) + geom_point(aes(color = Treatment)) + geom_smooth(aes(color = Treatment), method = 'glm') + theme_bw()

#Total Plant Cover 
macro_plant <- macro_plant %>% mutate(plantCover = rowSums(.[23:66]))

ggplot(data = macro_plant, aes(x = plantCover, y = Per.Total)) + geom_point(aes(color = Treatment)) + geom_smooth(aes(color = Treatment), method = 'glm') + theme_bw()

#microcystis

ggplot(data = macro_bsc, aes(x = Per.Total, y = Microcystis)) + geom_point(aes(color = Treatment)) + geom_smooth(method = 'glm') + theme_bw()

# Synechocystis

ggplot(data = macro_bsc, aes(x = Per.Total, y = Synechocystis)) + geom_point(aes(color = Treatment)) + geom_smooth(method = 'glm') + theme_bw()

#Phaeosphaeria

ggplot(data = macro_bulk, aes(x = Per.Total, y = Phaeosphaeria_mean)) + geom_point(aes(color = Treatment)) + geom_smooth(method = 'glm') + theme_bw()

# Geobacillus
bsc_plant <- bsc_plant %>% mutate(plantCover = rowSums(.[8:51]))
ggplot(data = bsc_plant, aes(x = plantCover, y = Geobacillus)) + geom_point(aes(color = Treatment)) + geom_smooth(method = 'glm') + theme_bw()

# Dechloromona
ggplot(data = bsc_plant, aes(x = plantCover, y = Dechloromonas)) + geom_point(aes(color = Treatment)) + geom_smooth(method = 'glm') + theme_bw()

#Sorangium
plant_bulk$Sorangium <- as.numeric(plant_bulk$Sorangium)
ggplot(data = plant_bulk, aes(x = plantCover, y = Sorangium)) + geom_point(aes(color = Treatment)) + geom_smooth(method = 'glm') + theme_bw()

#Gemmatoimonas
plant_bulk$Gemmatimonas <- as.numeric(plant_bulk$Gemmatimonas)
ggplot(data = plant_bulk, aes(x = plantCover, y = Gemmatimonas)) + geom_point(aes(color = Treatment)) + geom_smooth(method = 'glm') + theme_bw()

# Plancetomyces

ggplot(data = bsc, aes(x = treatment, y = Planctomyces)) + geom_boxplot(aes(fill = treatment))+ theme_bw()


# Bordetella
ggplot(data = bsc, aes(x = treatment, y = Bordetella)) + geom_boxplot(aes(fill = treatment))+ theme_bw()

# Geodermatophilus 
bulk$Geodermatophilus <- as.numeric(bulk$Geodermatophilus)
ggplot(data = bulk, aes(x = treatment, y = Geodermatophilus)) + geom_boxplot(aes(fill = treatment))+ theme_bw()

# EROBOT
ggplot(data = plants, aes(x = Treatment, y = EROBOT_mean)) + geom_boxplot(aes(fill = Treatment))+ theme_bw()

# SONOLE
ggplot(data = plants, aes(x = Treatment, y = SONOLE_mean)) + geom_boxplot(aes(fill = Treatment))+ theme_bw()

```

